Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-09-10 review_article.Rmd
introduction revision tweaks

<!-- Ways to visualise, whats our hypothesis -->
A common approach to communicate cancer statistics, is to display statistics on a map. This is a disease map: the statistic is mapped to colour and the geographic region is filled with this colour. The viewer would then be able to examine the spatial distribution of the disease incidence, where there is a trend in longitude or latitude, or rural vs urban, or coastal vs inland, or even specific hotspots of the disease. Visualising diseases on maps is often the first step in exploratory spatial data analysis and effectively helps in the formulation of hypotheses [@MTMSIH]. Disease maps help to present geographic patterns that may have been overlooked in a table, obscuring the geospatially related statistics [@SAMGIS].
By providing a visual representation of cancer outcomes, geographic patterns of disease are able to be identified and effectively addressed with public healh policy and actions.
@SE recognises one of the key challenges with mapping spatial patterns of disease is the design of visualisations.
This paper addresses the visualisation techniques and their applications to cancer statistics. Highlighting the differences and historic use of these displays.

<!-- Structure of the paper -->
The paper is organised as follows.  The next section describes the choropleth map which is the common approach to disease maps. Section XXX surveys atlases in use today. Section XXX describes an alternative display, the cartogram what may be useful for countries that have heterogeneously sized geographic units. The pros and cons of these approaches is discussed in Section XXX. Interactivity options are described in Section XXX, and the paper finishes with a discussion.

>>>>

<!-- Ways to visualise, whats our hypothesis -->
A common approach to communicate cancer statistics, is to display statistics on a map. This is a choropleth map: the statistic is mapped to colour and the geographic region is filled with this colour. The viewer would then be able to examine the spatial distribution of the disease incidence, where there is a trend in longitude or latitude, or rural vs urban, or coastal vs inland, or even specific hotspots of the disease. Visualising diseases on maps is often the first step in exploratory spatial data analysis and effectively helps in the formulation of hypotheses [@MTMSIH]. Disease maps help to present geographic patterns that may have been overlooked in a table, obscuring the geospatially related statistics [@SAMGIS].
By providing a visual representation of cancer outcomes, geographic patterns of disease are able to be identified and effectively addressed with public healh policy and actions.
@SE recognises one of the key challenges with mapping spatial patterns of disease is the design of visualisations.
This paper addresses the visualisation techniques and their applications to cancer statistics. Highlighting the differences and historic use of these displays.

<!-- Structure of the paper -->
The paper is organised as follows.  The next section describes the choropleth map which is the common approach to disease maps. Section XXX surveys atlases in use today. Section XXX describes an alternative display, the cartogram what may be useful for countries that have heterogeneously sized geographic units. The pros and cons of these approaches is discussed in Section XXX. Disease maps are ore useful when made interactive, and common options are described in Section XXX, along with a discussion of benefits and disadvantages. The last section summarises the paper and discusses future directions.
